Manuscript for MADA Project

### 2023-03-19 products/supplement.qmd
Part 3

        -   `Sept` folder: Contains processed data for September

            -   `processed_data_31701_Sept.rds`: Contains processed data for the 31701 zip code

            -   `processed_data_31705_Sept.rds`: Contains processed data for the 31705 zip code

            -   `processed_data_31707_Sept.rds`: Contains processed data for the 31707 zip code

        -   `Oct` folder: Contains processed data for October

            -   `processed_data_31701_Oct.rds`: Contains processed data for the 31701 zip code

            -   `processed_data_31705_Oct.rds`: Contains processed data for the 31705 zip code

            -   `processed_data_31707_Oct.rds`: Contains processed data for the 31707 zip code

        -   `Nov` folder: Contains processed data for November

            -   `processed_data_31701_Nov.rds`: Contains processed data for the 31701 zip code

            -   `processed_data_31705_Nov.rds`: Contains processed data for the 31705 zip code

            -   `processed_data_31707_Nov.rds`: Contains processed data for the 31707 zip code

        -   `Dec` folder: Contains processed data for December

            -   `processed_data_31701_Dec.rds`: Contains processed data for the 31701 zip code

            -   `processed_data_31705_Dec.rds`: Contains processed data for the 31705 zip code

            -   `processed_data_31707_Dec.rds`: Contains processed data for the 31707 zip code

        -   `Jan` folder: Contains processed data for January

            -   `processed_data_31701_Jan.rds`: Contains processed data for the 31701 zip code

            -   `processed_data_31705_Jan.rds`: Contains processed data for the 31705 zip code

            -   `processed_data_31707_Jan.rds`: Contains processed data for the 31707 zip code

        -   `Feb` folder: Contains processed data for February

            -   `processed_data_31701_Feb.rds`: Contains processed data for the 31701 zip code

            -   `processed_data_31705_Feb.rds`: Contains processed data for the 31705 zip code

            -   `processed_data_31707_Feb.rds`: Contains processed data for the 31707 zip code

@@

        -   `analysiscode1.R`: Contains the code an analysis of the total amount of African Americans with at least one COVID-19 vaccine in the 31701 zip code
        -   `readme.md`: provides a brief description of the analysis files

@@

    -   `Manuscript.qmd` file: Contains the manuscript for this project
    -   `My_Library.bib`: Bibliography for this project

@@

-   `results` folder:

>>>>

        -   `Zip_31701` folder: Contains processed data for the 31701 zip code

            -   `processed_data_31701_Sept.rds`: Contains processed data for the 31701 zip code during September, 2022

            -   `processed_data_31701_Oct.rds`: Contains processed data for the 31701 zip code during October, 2022

            -   `processed_data_31701_Nov.rds`: Contains processed data for the 31701 zip code during November, 2022

            -   `processed_data_31701_Dec.rds`: Contains processed data for the 31701 zip code during December, 2022

            -   `processed_data_31701_Jan.rds`: Contains processed data for the 31701 zip code during January, 2023

            -   `processed_data_31701_Feb.rds`: Contains processed data for the 31701 zip code during February, 2023

            -   `processed_combined_31701.rds`: Contains all vaccinations with all variables by month (September-February) for African Americans in the 31701 zip

        -   `Zip_31705` folder: Contains processed data for the 31705 zip code

            -   `processed_data_31705_Sept.rds`: Contains processed data for the 31705 zip code during September, 2022

            -   `processed_data_31705_Oct.rds`: Contains processed data for the 31705 zip code during October, 2022

            -   `processed_data_31705_Nov.rds`: Contains processed data for the 31705 zip code during November, 2022

            -   `processed_data_31705_Dec.rds`: Contains processed data for the 31705 zip code during December, 2022

            -   `processed_data_31705_Jan.rds`: Contains processed data for the 31705 zip code during January, 2022

            -   `processed_data_31705_Feb.rds`: Contains processed data for the 31705 zip code during Feb ruary, 2022

        -   `Zip_31707` folder: Contains processed data for the 31707 zip code

            -   `processed_data_31707_Sept.rds`: Contains processed data for the 31707 zip code during September, 2022

            -   `processed_data_31707_Oct.rds`: Contains processed data for the 31707 zip code during October, 2022

            -   `processed_data_31707_Nov.rds`: Contains processed data for the 31707 zip code during November, 2022

            -   `processed_data_31707_Dec.rds`: Contains processed data for the 31707 zip code during December, 2022

            -   `processed_data_31707_Jan.rds`: Contains processed data for the 31707 zip code during January, 2023

            -   `processed_data_31707_Feb.rds`: Contains processed data for the 31707 zip code during February, 2023

@@

        -   `analysiscode1.qmd`: Contains the code an analysis of the total amount of African Americans with at least one COVID-19 vaccine in all three target zip codes
        -   `analysiscode1.html`: Contains the output document from rendering `analysiscode1.qmd`
        -   `readme.md`: provides a brief description of the analysis files

@@

    -   `Manuscript.qmd` file: Contains the manuscript for this project

    -   `My_Library.bib`: Bibliography for this project

@@

-   `results` folder: Contains the graphs produced from rendering the analysis `analysiscode1.qmd`

    -   `Black_Vax_Total.png`: Contains a line graph with all three zip codes plotted for the African American populations

    -   `Black_Vax_Total_31701.png` : A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31701 zip code

    -   `Black_Vax_Total_31705.png` : A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31705 zip code

    -   `Black_Vax_Total_31707.png`: A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31707 zip code
